Master's thesis Computer Science\\ (Chair: Databases, Track: Information System Engineering)

### 2014-09-29 report/FrontBackmatter/Titlepage.tex
voorkant
Dolf erbij

\committee{Dr. ir. Djoerd Hiemstra (UT/Databases)\\
Sander Bockting, Msc (Avanade Netherlands B.V.)\\
}	
\date{\today}
\num{}

\supervisors{Dr. ir. Djoerd Hiemstra (UT/Databases)\\
Sander Bockting (Avanade Netherlands B.V.)}    
\end{titlepage}
\maketitle

>>>>

\committee{
Dr. ir. Djoerd Hiemstra (University of Twente / Databases)\\
Ir. Dolf Trieschnigg (University of Twente / Human Media Interaction)\\
Sander Bockting, Msc (Avanade Netherlands B.V.)\\
}	
\date{\today}
\num{}

\supervisors{
Dr. ir. Djoerd Hiemstra (University of Twente / Databases)\\
Sander Bockting (Avanade Netherlands B.V.)
}    
\end{titlepage}
\maketitle
\clearpage
